Arrows for Parallel Computations

### 2017-08-15 paper/content/benchmarks.tex
minor

Jacobi sum test or APRCL is also a primality test, that however,
guarantees the correctness of the result. It is probabilistic in the
sense that its run time is not certain. Unlike \rmtest, the subtests
of Jacobi sum test have very different durations. \citet{lobachev-phd}
discuss some optimisations of parallel APRCL. Generic parallel
implementation of \rmtest and APRCL were presented in \citet{Lobachev2012}.

``Gentleman'' is a standard Eden test program, developed
for their |torus| skeleton. It implements a parallel matrix
multiplication \citep{Gentleman1978}. We ported its latest Eden
version \citep{Loogen2012} to PArrows and changed it so that it runs multiple |torus| computations in parallel with |parMap|.

>>>>

Jacobi sum test or APRCL is also a primality test, that however,
guarantees the correctness of the result. It is probabilistic in the
sense that its run time is not certain. Unlike \rmtest, the subtests
of Jacobi sum test have very different durations. \citet{lobachev-phd}
\olcomment{discuss some optimisations of parallel APRCL.} Generic parallel
implementation of \rmtest and APRCL were presented in \citet{Lobachev2012}.

``Gentleman'' is a standard Eden test program, developed
for their |torus| skeleton. It implements a parallel matrix
multiplication \citep{Gentleman1978}. We ported its latest Eden
version \citep{Loogen2012} to PArrows.
